scikit-image: Image processing in Python

### 2014-03-31 paper.tex
Use citep instead of cite

The library allows students in image processing to learn algorithms in a
hands-on fashion by adjusting parameters and modifying code. In addition, a
\texttt{novice} module is provided, not only for teaching programming in the
\textquotedbl{}turtle graphics\textquotedbl{} paradigm, but also to familiarize users with image
concepts such as color and dimensionality. Furthermore, the project
takes part in the yearly Google Summer of Code \cite{gsoc} program, where
students learn about image processing and software engineering through
contributing to the project.
\item

@@

\PY{n}{ax3}\PY{o}{.}\PY{n}{imshow}\PY{p}{(}\PY{n}{image}\PY{p}{,} \PY{n}{cmap}\PY{o}{=}\PY{n}{plt}\PY{o}{.}\PY{n}{cm}\PY{o}{.}\PY{n}{gray}\PY{p}{)}
\PY{n}{ax3}\PY{o}{.}\PY{n}{autoscale}\PY{p}{(}\PY{n+nb+bp}{False}\PY{p}{)}
\PY{n}{ax3}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{coordinates}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{,}
         \PY{n}{coordinates}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{]}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{r.}\PY{l+s}{\PYZsq{}}\PY{p}{)}
\PY{n}{ax3}\PY{o}{.}\PY{n}{set\PYZus{}title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Peak local maxima}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{24}\PY{p}{)}
\PY{n}{ax3}\PY{o}{.}\PY{n}{axis}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{off}\PY{l+s}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}
Next, a Canny filter (\texttt{filter.canny}) \cite{Canny} detects the edge of each coin.\begin{Verbatim}[commandchars=\\\{\},fontsize=\footnotesize]
\PY{c}{\PYZsh{} Detect edges.}
\PY{k+kn}{from} \PY{n+nn}{skimage} \PY{k+kn}{import} \PY{n+nb}{filter}

@@

The scikit-image project started in August of 2009 and has received
contributions from more than 100 individuals \cite{ohloh}.  The package can be
installed from, amongst other sources, the Python Package Index, Continuum
Anaconda \cite{anaconda}, Enthought Canopy \cite{canopy}, Python(x,y) \cite{pythonxy},
NeuroDebian \cite{neurodebian} and GNU/Linux distributions such as Ubuntu \cite{ubuntu}.
In March 2014 alone, the package was downloaded more than 5000 times from the
Python Package Index \cite{pypi}.

@@

scikit-image represents images as NumPy arrays \cite{numpy}, the de facto standard
for storage of multi-dimensional data in scientific Python. Each array has a
dimensionality, such as 2 for a 2-D grayscale image, 3 for a 2-D multi-
channel image, or 4 for a 3-D multi-channel image; a shape, such as \$(M, N, 3)\$
for an RGB color image with \$M\$ vertical and \$N\$ horizontal pixels; and a
numeric data type, such as \texttt{float} for continuous-valued pixels and \texttt{uint8}
for 8-bit pixels. Our use of NumPy arrays as the fundamental data structure
maximizes compatibility with the rest of the scientific Python ecosystem.
Data can be passed as-is to other tools such as NumPy, SciPy, matplotlib,
scikit-learn \cite{scikit-learn}, Mahotas {[}Mahotas{]}, OpenCV, and more.

@@

The library is licensed under the \emph{Modified BSD license}, which allows
unrestricted redistribution for any purpose as long as copyright notices
and disclaimers of warranty are maintained \cite{BSD}. It is compatible with GPL
licenses, so users of scikit-image can choose to make their code available
under the GPL. However, unlike the GPL, it does not require users to
open-source derivative work (BSD is not a so-called copyleft license). Thus,
scikit-image can also be used in closed-source, commercial environments.

The development team of scikit-image is an open community that collaborates on
the \emph{GitHub} \cite{GitHub} platform for issue tracking, code review, and release
management. \emph{Google Groups} \cite{GoogleGroups} is used as a public discussion
forum for user support, community development, and announcements.

scikit-image complies with the PEP8 coding style standard \cite{PEP8} and the NumPy
documentation format \cite{NumpyDoc} in order to provide a consistent, familiar user
experience across the library similar to other scientific Python packages. As
mentioned earlier, the data representation used is \emph{n}-dimensional
NumPy arrays, which guarantees universal interoperability
within the scientific Python ecosystem. The majority of the scikit-image API is
intentionally designed as a functional interface which allows one to simply
apply one function to the output of another. This modular approach also lowers the
barrier of entry for new contributors, since one only needs to master a small
part of the entire library in order to make an addition.

We ensure high code quality by a thorough review process using the pull request
interface on GitHub. The source code is mainly written in Python, although
certain performance critical sections are implemented in Cython, an
optimising static compiler for Python
\cite{Cython}.  scikit-image aims to achieve full unit test coverage, which is above
85\% as of release 0.10 and continues to rise. A continuous integration system
(\cite{TravisCI}, \cite{Coveralls}) automatically checks each commit for unit test
coverage and failures on both Python 2 and Python 3. Additionally, the code is
analyzed by flake8 \cite{flake8} to ensure compliance with the PEP8 coding style
standards \cite{PEP8}. Finally, the properties of each public function are
documented thoroughly in an API reference guide, embedded as Python
docstrings and accessible through the official project homepage or an
interactive
Python console. Short usage examples are
typically included inside the docstrings, and new features are accompanied by longer,
self-contained example scripts added to the narrative documentation and
compiled to a gallery on the project website. We use Sphinx
\cite{Sphinx} to automatically generate both library documentation and the website.

The development master branch is fully functional at all times and can be
obtained from GitHub \cite{SourceCode}. The community releases major updates as
stable versions approximately every six months \cite{Versioning}. Major releases
include new features, while minor releases typically contain only bug fixes.
Users are notified about API-breaking changes by deprecation warnings one full
major release before they are applied.

@@

Often, a disproportionately large component of research involves dealing with
various image data-types, color representations, and file format
conversion. scikit-image offers robust tools for converting between image
data-types (\cite{DirectX}, \cite{OpenGL}, \cite{GraphicsGemsI}) and to do file input/output
(I/O) operations.  Our purpose is to allow investigators to focus their time on
research, instead of expending effort on mundane low-level tasks.

The package includes a number of algorithms with broad applications across
image processing research, from computer vision to medical image analysis. We
refer the reader to the current API documentation for a full listing of current
capabilities \cite{APIdocs}. In this section we illustrate two real-world usage
examples of scikit-image in scientific research.

@@

Next, in regenerative medicine research, scikit-image is used to monitor the
regeneration of spinal cord cells in zebrafish embryos (Figure \DUrole{ref}{profile}).
This process has important implications for the treatment of spinal cord
injuries in humans (\cite{Bhatt04,Thuret06}).

@@

Demonstrating the utility and ease-of-use of scikit-image, thirteen-year-old
Rishab Gargeya of the Harker School won the Synopsys Silicon
Valley Science and Technology Championship using scikit-image in
his project, \textquotedbl{}A software based approach for automated pathology diagnosis of
diabetic retinopathy in the human retina\textquotedbl{} \cite{sciencefair}.

We have also delivered
image processing tutorials using scikit-image at various
annual scientific Python conferences, such as EuroSciPy \cite{euroscipy2013}, PyData
2012 \cite{pydata2012} and SciPy India
2012). Course materials for some of these sessions are found in
\cite{scipylecturenotes} and are licensed under the permissive \cite{cc-by}
license.  These typically include an introduction to the package and provide
intuitive, hands-on introductions to image processing concepts. The well
documented application programming interface (API) along with tools that
facilitate visualization contribute to the learning experience, and make it
easy to investigate the effect of different algorithms and parameters.
For example, when investigating denoising, it is easy to observe the difference
between applying a median filter (\texttt{filter.rank.median}) and a
Gaussian filter (\texttt{filter.gaussian\_filter}),
demonstrating that a median filter preserves straight lines much better.

@@

BT Imaging \cite{BTImaging} designs and builds tools that use photoluminescence (PL)
imaging for photovoltaic applications. PL imaging can characterize
the quality of multicrystalline silicon wafers by illuminating defects
that are not visible under standard viewing conditions. The left panel of Figure \DUrole{ref}{PL} shows an optical image of a
silicon wafer, and the center panel shows the same wafer using PL imaging.
In the right panel, the wafer defects and impurities have been detected through automated
image analysis. scikit-image plays a key role in the image processing
pipeline. For example, a Hough transform (\texttt{transform.hough\_line}) finds the wafer edges
in order to segment the wafer from the background. scikit-image
is also used for feature extraction. Crystal defects
(dislocations) are detected using a band-pass filter, which is implemented as a
Difference of Gaussians (\texttt{filter.gaussian\_filter}).

@@

scikit-image is also applied in a commercial setting for biometric security applications.
AICBT Ltd uses multispectral imaging to detect when a person
attempts to conceal their identity using a facial mask \cite{AICBT}.
scikit-image performs file I/O (\texttt{io.imread}), histogram equalization
(\texttt{exposure.equalize\_hist}), and aligns a visible wavelength image with
a thermal image (\texttt{transform.AffineTransform}). The system determines
the surface temperature of a subject's skin and detects situations where the
face is being obscured.

@@

\textquotedbl{}Oriented FAST and rotated BRIEF\textquotedbl{} (ORB) features \cite{ORB} are detected in both
images.  Each feature yields a binary descriptor; those are used to find the
putative matches shown in Figure~\DUrole{ref}{pano} B.\begin{Verbatim}[commandchars=\\\{\},fontsize=\footnotesize]
\PY{k+kn}{from} \PY{n+nn}{skimage.feature} \PY{k+kn}{import} \PY{n}{ORB}\PY{p}{,} \PY{n}{match\PYZus{}descriptors}

@@

To filter the matches, we apply RANdom SAmple Consensus (RANSAC) \cite{ransac}, a
common method for outlier rejection. This iterative process estimates
transformation models based on randomly chosen subsets of matches, finally
selecting the model which corresponds best with the majority of matches.  The
new matches are shown in Figure~\DUrole{ref}{pano} C.\begin{Verbatim}[commandchars=\\\{\},fontsize=\footnotesize]
\PY{k+kn}{from} \PY{n+nn}{skimage.transform} \PY{k+kn}{import} \PY{n}{ProjectiveTransform}
\PY{k+kn}{from} \PY{n+nn}{skimage.measure} \PY{k+kn}{import} \PY{n}{ransac}

@@

To blend images smoothly we make use of the open source package Enblend
\cite{Enblend}, which in turn employs multi-resolution splines and Laplacian
pyramids \cite{burt_adelson_0}, \cite{burt_adelson_1}.  The final panorama is shown in
Figure~\DUrole{ref}{pano} E.\begin{figure*}[bht]\noindent\makebox[\textwidth][c]{\includegraphics[scale=1.00]{pano-full.png}}
\caption{An example application of scikit-image: image registration and warping.
A: Original photographs by François Malan, taken in Petra, Jordan. License:
CC-BY.
B: Putative matches computed from ORB binary features.
C: Matches filtered using RANSAC.
D: The second input frame (center) is warped to align with the first input
frame (left). The two are averaged for a simple blend (right).
E :The final panorama image, registered and warped using scikit-image,
blended with Enblend.
\DUrole{label}{pano}}
\end{figure*}

>>>>

The library allows students in image processing to learn algorithms in a
hands-on fashion by adjusting parameters and modifying code. In addition, a
\texttt{novice} module is provided, not only for teaching programming in the
\textquotedbl{}turtle graphics\textquotedbl{} paradigm, but also to familiarize users with image
concepts such as color and dimensionality. Furthermore, the project
takes part in the yearly Google Summer of Code \citep{gsoc} program, where
students learn about image processing and software engineering through
contributing to the project.
\item

@@

\PY{n}{ax3}\PY{o}{.}\PY{n}{imshow}\PY{p}{(}\PY{n}{image}\PY{p}{,} \PY{n}{cmap}\PY{o}{=}\PY{n}{plt}\PY{o}{.}\PY{n}{cm}\PY{o}{.}\PY{n}{gray}\PY{p}{)}
\PY{n}{ax3}\PY{o}{.}\PY{n}{autoscale}\PY{p}{(}\PY{n+nb+bp}{False}\PY{p}{)}
\PY{n}{ax3}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{coordinates}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{,}
         \PY{n}{coordinates}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{]}\PY{p}{,} \PY{l+s}{\PYZsq{}}\PY{l+s}{r.}\PY{l+s}{\PYZsq{}}\PY{p}{)}
\PY{n}{ax3}\PY{o}{.}\PY{n}{set\PYZus{}title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Peak local maxima}\PY{l+s}{\PYZsq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{24}\PY{p}{)}
\PY{n}{ax3}\PY{o}{.}\PY{n}{axis}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{off}\PY{l+s}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}
Next, a Canny filter (\texttt{filter.canny}) \citep{Canny} detects the edge of each coin.\begin{Verbatim}[commandchars=\\\{\},fontsize=\footnotesize]
\PY{c}{\PYZsh{} Detect edges.}
\PY{k+kn}{from} \PY{n+nn}{skimage} \PY{k+kn}{import} \PY{n+nb}{filter}

@@

The scikit-image project started in August of 2009 and has received
contributions from more than 100 individuals \citep{ohloh}.  The package can be
installed from, amongst other sources, the Python Package Index, Continuum
Anaconda \citep{anaconda}, Enthought Canopy \citep{canopy}, Python(x,y) \citep{pythonxy},
NeuroDebian \citep{neurodebian} and GNU/Linux distributions such as Ubuntu \citep{ubuntu}.
In March 2014 alone, the package was downloaded more than 5000 times from the
Python Package Index \citep{pypi}.

@@

scikit-image represents images as NumPy arrays \citep{numpy}, the de facto standard
for storage of multi-dimensional data in scientific Python. Each array has a
dimensionality, such as 2 for a 2-D grayscale image, 3 for a 2-D multi-
channel image, or 4 for a 3-D multi-channel image; a shape, such as \$(M, N, 3)\$
for an RGB color image with \$M\$ vertical and \$N\$ horizontal pixels; and a
numeric data type, such as \texttt{float} for continuous-valued pixels and \texttt{uint8}
for 8-bit pixels. Our use of NumPy arrays as the fundamental data structure
maximizes compatibility with the rest of the scientific Python ecosystem.
Data can be passed as-is to other tools such as NumPy, SciPy, matplotlib,
scikit-learn \citep{scikit-learn}, Mahotas \citep{Mahotas}, OpenCV, and more.

@@

The library is licensed under the \emph{Modified BSD license}, which allows
unrestricted redistribution for any purpose as long as copyright notices
and disclaimers of warranty are maintained \citep{BSD}. It is compatible with GPL
licenses, so users of scikit-image can choose to make their code available
under the GPL. However, unlike the GPL, it does not require users to
open-source derivative work (BSD is not a so-called copyleft license). Thus,
scikit-image can also be used in closed-source, commercial environments.

The development team of scikit-image is an open community that collaborates on
the \emph{GitHub} \citep{GitHub} platform for issue tracking, code review, and release
management. \emph{Google Groups} \citep{GoogleGroups} is used as a public discussion
forum for user support, community development, and announcements.

scikit-image complies with the PEP8 coding style standard \citep{PEP8} and the NumPy
documentation format \citep{NumpyDoc} in order to provide a consistent, familiar user
experience across the library similar to other scientific Python packages. As
mentioned earlier, the data representation used is \emph{n}-dimensional
NumPy arrays, which guarantees universal interoperability
within the scientific Python ecosystem. The majority of the scikit-image API is
intentionally designed as a functional interface which allows one to simply
apply one function to the output of another. This modular approach also lowers the
barrier of entry for new contributors, since one only needs to master a small
part of the entire library in order to make an addition.

We ensure high code quality by a thorough review process using the pull request
interface on GitHub. The source code is mainly written in Python, although
certain performance critical sections are implemented in Cython, an
optimising static compiler for Python
\citep{Cython}.  scikit-image aims to achieve full unit test coverage, which is above
85\% as of release 0.10 and continues to rise. A continuous integration system
\citep{TravisCI,Coveralls} automatically checks each commit for unit test
coverage and failures on both Python 2 and Python 3. Additionally, the code is
analyzed by flake8 \citep{flake8} to ensure compliance with the PEP8 coding style
standards \citep{PEP8}. Finally, the properties of each public function are
documented thoroughly in an API reference guide, embedded as Python
docstrings and accessible through the official project homepage or an
interactive
Python console. Short usage examples are
typically included inside the docstrings, and new features are accompanied by longer,
self-contained example scripts added to the narrative documentation and
compiled to a gallery on the project website. We use Sphinx
\citep{Sphinx} to automatically generate both library documentation and the website.

The development master branch is fully functional at all times and can be
obtained from GitHub \citep{SourceCode}. The community releases major updates as
stable versions approximately every six months \citep{Versioning}. Major releases
include new features, while minor releases typically contain only bug fixes.
Users are notified about API-breaking changes by deprecation warnings one full
major release before they are applied.

@@

Often, a disproportionately large component of research involves dealing with
various image data-types, color representations, and file format
conversion. scikit-image offers robust tools for converting between image
data-types \citep{DirectX,OpenGL,GraphicsGemsI} and to do file input/output
(I/O) operations.  Our purpose is to allow investigators to focus their time on
research, instead of expending effort on mundane low-level tasks.

The package includes a number of algorithms with broad applications across
image processing research, from computer vision to medical image analysis. We
refer the reader to the current API documentation for a full listing of current
capabilities \citep{APIdocs}. In this section we illustrate two real-world usage
examples of scikit-image in scientific research.

@@

Next, in regenerative medicine research, scikit-image is used to monitor the
regeneration of spinal cord cells in zebrafish embryos (Figure \DUrole{ref}{profile}).
This process has important implications for the treatment of spinal cord
injuries in humans \citep{Bhatt04,Thuret06}.

@@

Demonstrating the utility and ease-of-use of scikit-image, thirteen-year-old
Rishab Gargeya of the Harker School won the Synopsys Silicon
Valley Science and Technology Championship using scikit-image in
his project, \textquotedbl{}A software based approach for automated pathology diagnosis of
diabetic retinopathy in the human retina \citep{sciencefair}.

We have also delivered
image processing tutorials using scikit-image at various
annual scientific Python conferences, such as EuroSciPy \citep{euroscipy2013}, PyData
2012 \citep{pydata2012} and SciPy India
2012). Course materials for some of these sessions are found in
\citep{scipylecturenotes} and are licensed under the permissive \citep{cc-by}
license.  These typically include an introduction to the package and provide
intuitive, hands-on introductions to image processing concepts. The well
documented application programming interface (API) along with tools that
facilitate visualization contribute to the learning experience, and make it
easy to investigate the effect of different algorithms and parameters.
For example, when investigating denoising, it is easy to observe the difference
between applying a median filter (\texttt{filter.rank.median}) and a
Gaussian filter (\texttt{filter.gaussian\_filter}),
demonstrating that a median filter preserves straight lines much better.

@@

BT Imaging \citep{BTImaging} designs and builds tools that use photoluminescence (PL)
imaging for photovoltaic applications. PL imaging can characterize
the quality of multicrystalline silicon wafers by illuminating defects
that are not visible under standard viewing conditions. The left panel of Figure \DUrole{ref}{PL} shows an optical image of a
silicon wafer, and the center panel shows the same wafer using PL imaging.
In the right panel, the wafer defects and impurities have been detected through automated
image analysis. scikit-image plays a key role in the image processing
pipeline. For example, a Hough transform (\texttt{transform.hough\_line}) finds the wafer edges
in order to segment the wafer from the background. scikit-image
is also used for feature extraction. Crystal defects
(dislocations) are detected using a band-pass filter, which is implemented as a
Difference of Gaussians (\texttt{filter.gaussian\_filter}).

@@

scikit-image is also applied in a commercial setting for biometric security applications.
AICBT Ltd uses multispectral imaging to detect when a person
attempts to conceal their identity using a facial mask \citep{AICBT}.
scikit-image performs file I/O (\texttt{io.imread}), histogram equalization
(\texttt{exposure.equalize\_hist}), and aligns a visible wavelength image with
a thermal image (\texttt{transform.AffineTransform}). The system determines
the surface temperature of a subject's skin and detects situations where the
face is being obscured.

@@

\textquotedbl{}Oriented FAST and rotated BRIEF\textquotedbl{} (ORB) features \citep{ORB} are detected in both
images.  Each feature yields a binary descriptor; those are used to find the
putative matches shown in Figure~\DUrole{ref}{pano} B.\begin{Verbatim}[commandchars=\\\{\},fontsize=\footnotesize]
\PY{k+kn}{from} \PY{n+nn}{skimage.feature} \PY{k+kn}{import} \PY{n}{ORB}\PY{p}{,} \PY{n}{match\PYZus{}descriptors}

@@

To filter the matches, we apply RANdom SAmple Consensus (RANSAC) \citep{ransac}, a
common method for outlier rejection. This iterative process estimates
transformation models based on randomly chosen subsets of matches, finally
selecting the model which corresponds best with the majority of matches.  The
new matches are shown in Figure~\DUrole{ref}{pano} C.\begin{Verbatim}[commandchars=\\\{\},fontsize=\footnotesize]
\PY{k+kn}{from} \PY{n+nn}{skimage.transform} \PY{k+kn}{import} \PY{n}{ProjectiveTransform}
\PY{k+kn}{from} \PY{n+nn}{skimage.measure} \PY{k+kn}{import} \PY{n}{ransac}

@@

To blend images smoothly we make use of the open source package Enblend
\citep{Enblend}, which in turn employs multi-resolution splines and Laplacian
pyramids \citep{burt_adelson_0,burt_adelson_1}.  The final panorama is shown in
Figure~\DUrole{ref}{pano} E.\begin{figure*}[bht]\noindent\makebox[\textwidth][c]{\includegraphics[scale=1.00]{pano-full.png}}
\caption{An example application of scikit-image: image registration and warping.
A: Original photographs by François Malan, taken in Petra, Jordan. License:
CC-BY.
B: Putative matches computed from ORB binary features.
C: Matches filtered using RANSAC.
D: The second input frame (center) is warped to align with the first input
frame (left). The two are averaged for a simple blend (right).
E :The final panorama image, registered and warped using scikit-image,
blended with Enblend.
\DUrole{label}{pano}}
\end{figure*}
